Inference of seasonal forcings on reproduction numbers during epidemics

### 2020-04-18 PaperDraft.Rmd
Describe the data

@@

$$ \beta^T = [-0.23198507 -0.05391226  0.26336295 -0.03586852] $$

>>>>

### Data

We sourced the following data:

- Italian case data aggregated per province from the Italian Civil Protection
  Department (DPC)
- 2017 demographic data for Italian provinces from Eurostat, via the `restatapi` package
- Weather data from NOAA's network of stations, via the `worldmet` package

A total of $102$ provinces were included in the analysis. This is all provinces
except those located in the region of Sardinia. The provinces in Sardinia were
excluded because of a mismatch between the demographic data and the case data,
due to a recent political reorganization in Sardinia.

A total of $19$ dates were included in the analysis, starting from the first date
of February 24, 2020 present in the data and concluding on March 13, 2020.
Although more dates are available, we felt that the dramatic interventions in
Italy after March 13 reduced the relevance of seasonal forcings on transmission.

A total of $4$ demographic and climatic features were included in the analysis:
air temperature, relative humidity, GDP per capita, and population density. The
demographic features are included as control so that the inferred coefficients
for weather are not due to spurious correlations with demographics, as Northern
Italy is generally denser, richer, and cooler on average than Southern Italy.

@@

$$ \beta^T = \begin{bmatrix} -0.23198507 & -0.05391226 & 0.26336295 & -0.03586852 \end{bmatrix} $$
